Supplementary Information

### 2021-06-03 doc/manuscript/ForestGEO_treerings_SI.Rmd
remove recruitment and decadal figures from SI (move to doc/supplementary_figures)
#130

#decadal plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/decadal_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/tree-rings_global-change/decadal_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/decadal_plots/")

#recruitment plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/recruitment_years/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO_dendro/data_processed/", "^Recrutement_years_.+[.]png$",  full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/recruitment_years/")

@@

## `r recruitment_plot_BCNM_legend`

![`r recruitment_plot_BCNM_legend` `r recruitment_generic_legend` "Heartrot was common at this site, implying that recruitment years are overestimated for some trees."](tables_figures/SI_figures/recruitment_years/Recrutement_years_BCI.png){ width=47% }

\newpage
## `r recruitment_plot_HKK_legend`

![`r recruitment_plot_HKK_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_HKK.png){ width=47% }

\newpage
## `r recruitment_plot_SCBI_legend`

![`r recruitment_plot_SCBI_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_SCBI.png){ width=90% }

## `r recruitment_plot_LDW_legend`

![`r recruitment_plot_LDW_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_LillyDickey.png){ width=47% }

\newpage
## `r recruitment_plot_HF_legend`

![`r recruitment_plot_HF_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_HarvardForest.png){ width=47% }

\newpage
## `r recruitment_plot_ZOF_legend`

![`r recruitment_plot_ZOF_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_Zofin.png){ width=47% }

\newpage
## `r recruitment_plot_NIO_legend`

![`r recruitment_plot_NIO_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_Niobara.png){ width=47% }

\newpage
## `r recruitment_plot_LT_legend`

![`r recruitment_plot_LT_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_NewMexico.png){ width=47% }

\newpage
## `r recruitment_plot_CB_legend`

![`r recruitment_plot_CB_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_CedarBreaks.png){ width=47% }

\newpage
## `r recruitment_plot_SC_legend`

![`r recruitment_plot_SC_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_ScottyCreek.png){ width=47% }

\newpage 
## `r SCBI_traditional_comparison_legend`
**Precipitation**

@@

\newpage
## `r decadal_plot_BCNM_legend`

![`r decadal_plot_BCNM_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/BCI.png){ width=100% }

\newpage
## `r decadal_plot_HKK_legend`

![`r decadal_plot_HKK_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/HKK.png){ width=100% }

\newpage
## `r decadal_plot_SCBI_legend`

![`r decadal_plot_SCBI_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/SCBI.png){ width=100% }

\newpage
## `r decadal_plot_LDW_legend`

![`r decadal_plot_LDW_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/LD.png){ width=100% }

\newpage
## `r decadal_plot_HF_legend`

![`r decadal_plot_HF_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/HF.png){ width=100% }

\newpage
## `r decadal_plot_ZOF_legend`

![`r decadal_plot_ZOF_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/ZN.png){ width=100% }

\newpage
## `r decadal_plot_NIO_legend`

``` {r eval=FALSE}
![`r decadal_plot_NIO_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/NIO.png){ width=100% }
```

\newpage
## `r decadal_plot_LT_legend`

![`r decadal_plot_LT_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/NM.png){ width=100% }

\newpage
## `r decadal_plot_CB_legend`

![`r decadal_plot_CB_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/CB.png){ width=100% }

\newpage
## `r decadal_plot_SC_legend`

![`r decadal_plot_SC_legend` `r decadal_generic_legend`](tables_figures/SI_figures/decadal_plots/SC.png){ width=100% }

>>>>

#decadal plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/supplementary_figures/decadal_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/tree-rings_global-change/decadal_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/supplementary_figures/decadal_plots/")

#recruitment plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/supplementary_figures/recruitment_years/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO_dendro/data_processed/", "^Recrutement_years_.+[.]png$",  full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/supplementary_figures/recruitment_years/")

@@

## `r SCBI_traditional_comparison_legend`
**Precipitation**

@@
